---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# tee

The goal of tee is to run R code in an isolated session, or arbitrary scripts, and log the output to a file.  It is similar to the `tee` utility, but relies on [*callr*](https://github.com/r-lib/callr) and [*processx*](https://github.com/r-lib/processx). All systems where these packages work (including Windows) are supported.

Works for me.


## Installation

You can install *tee* from GitHub:

``` r
# install.packages("remotes")
remotes::install_local("krlmlr/tee")
```

## Example

The `r_tee()` function has (almost) the same signature as `callr::r()` but supports a `tee` argument of type `character`. If set, all output will be written to the file(s) specified in the `tee` argument.

```{r example}
library(tee)
ret <- r_tee(function() { print("Hi!"); 42 }, tee = "hi.log")
ret
readLines("hi.log")
```

```{r cleanup, include = FALSE}
unlink("hi.log")
```
